% This file contains definitions of various fields used
% in various places throughout the thesis (in the title
% pages mostly). Whatever isn't define here has some
% default (and usually irrelevant) text.

\authorEnglish{Ohad Levy-Or}
\authorHebrew{אוהד לוי-אור}

\titleEnglish{Novel Class of Expected Value Bounds and Applications in Belief Space Planning}
\titleHebrew{משפחה חדשה של חסמים על תוכלת ושימושים בתכנון תחת אי-ודאות}

\disciplineEnglish{Autonomous Systems and Robotics}
\disciplineHebrew{מערכות אוטונומיות ורובוטיקה}

\supervisionEnglish{This research was carried out under the supervision of Prof. Vadim Indelman, in the Technion Autonomous Systems and Robotics Program.\\[\baselineskip]
The author of this thesis states that the research, including the collection, processing and presentation of data, addressing and comparing to previous research, etc., was done entirely in an honest way, as expected from scientific research that is conducted according to the ethical standards of the academic world. Also, reporting the research and its results in this thesis was done in an honest and complete manner, according to the same standards.}
\supervisionHebrew{המחקר בוצע בהנחייתו של פרופסור ואדים אינדלמן, בתוכנית למערכות אוטונומיות ורובוטיקה.
	\\[\baselineskip]
מחבר חיבור זה מצהיר כי המחקר, כולל איסוף הנתונים, עיבודם והצגתם, התייחסות והשוואה למחקרים קודמים וכו', נעשה כולו בצורה ישרה, כמצופה ממחקר מדעי המבוצע לפי אמות המידה האתיות של העולם האקדמי. כמו כן, הדיווח על המחקר ותוצאותיו בחיבור זה נעשה בצורה ישרה ומלאה, לפי אותן אמות מידה.}

\GregorianDateEnglish{September 2024}
\GregorianDateHebrew{ספטמבר \textenglish{2024}}
\JewishDateEnglish{Elul 5784}
\JewishDateHebrew{אלול התשפ"ד}

\financialAcknowledgementEnglish{The Technion's funding of this research is hereby acknowledged.}
\financialAcknowledgementHebrew{הכרת תודה מסורה לטכניון על מימון מחקר זה.}

\publicationInfoEnglish{%

Some results in this thesis have been published as articles by the author and research collaborators in conferences and journals during the course of the author's doctoral research period, the most up-to-date versions of which being:

\butcheredbibliography{front/pubinfo.bib}
}

\publicationInfoHebrew{%

חלק מן התוצאות בחיבור זה פורסמו כמאמרים מאת המחבר ושותפיו למחקר בכנסים ובכתבי-עת במהלך תקופת מחקר הדוקטורט של המחבר, אשר גרסאותיהם העדכניות ביותר הינן:%

\begin{otherlanguage}{english}%
\butcheredbibliography{front/pubinfo.bib}
\end{otherlanguage}%
}

\addbibresource{back/general.bib}
% \thesisbibstyle{trad-alpha}
